Hydras \& Co.: Formalized mathematics in Coq\\ for inspiration and entertainment

### 2022-05-08 doc/JFLA2022/Slides/Slides.tex
changes to JFLA slides

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}
  \frametitle{The \Hydras project}
  \begin{block}{}
    \begin{itemize}
   \item Experimental platform for the  development of \textcolor{lookcolor}{maintained} and \textcolor{lookcolor}{documented} libraries of formal proofs.
    \item A project of \community, developped on Github
      \begin{itemize}
      \item CI/CD
        \item Tools for collaboration (issues, PR, etc.)
        \end{itemize}
           \item book in pdf (300p), generated  with \textcolor{lookcolor}{\alectr} and \LaTeX, continuously updated and deployed
    \end{itemize}
  \end{block}
  \begin{block}{Contents}
    \begin{itemize}
    \item Evolved version  of two contributions: \textcolor{plugincolor}{Cantor} and \textcolor{plugincolor}{Additions}
    \item Maintenance of \textcolor{plugincolor}{Ackermann}
      (part of Russel O'Connor's \textcolor{plugincolor}{Goedel})
    \item Bridge to \textcolor{plugincolor}{Gaia} (José Grimm) (\emph{in construction})

@@

  \begin{scope}[yshift=2.0cm, xshift=1.7cm] 
     \node[ellipse, dotted, fill=orange!20, minimum height=0.5cm,minimum width=1.5cm] (settheory) { Set theory\footnote{N. Bourbaki}};
      \node[ellipse, dotted, fill=orange!20, minimum height=0.5cm,minimum width=1.5cm, left of=settheory, node distance=8.4cm] (prooftheory) { Proof theory\footnote{K. Schutte, J. Ketonen, R. Solovay, L. Kirby \& J. Paris}};
\end{scope}

\begin{scope}[yshift=1.0cm, xshift=-1.5cm]
   \node[ellipse, dotted, draw= black!20,fill=green!20,minimum height=0.5cm,minimum width=1.5cm] (acl2) { [ACL2]\footnote{P. Manolios \&  D. Vroon}};   
\end{scope}

@@

\draw[->] (equations) -- (hydras) ;
\draw[->] (mathcomp) -- (gaia) ;
\draw[->] (mathcomp) -- (chains) ;
\draw[->] (paramcoq.south) -- (chains) ;
\draw[->] (pockcc) -- (goedelcc) ;
\draw[dotted, ->] (prooftheory) -- (hydras);
\draw[dotted, ->] (settheory) -- (cats);

\end{tikzpicture}
}
\caption{Genealogy and dependencies for \Hydras packages.}
  \label{fig:genealogy}
\end{figure}
\end{frame}

@@

\begin{frame}
   \begin{block}{An example-driven book}
    \begin{itemize}
    \item The structure is determined by the presented topics (discrete math, algorithmics, etc.). \coq technology (formalization and proof patterns) is presented when needed.
    \item No need to be complete (there is already a reference manual)
    \item No need to introduce \coq (there are already a lot of initiation books and tutorials)
    \item Allow to compare several different formalizations of a given notion, and several proofs of the same theorem.
      \item Show also interesting dead ends (formalization, tactics, proof structure).
    \end{itemize}
  \end{block}
  % \begin{block}{Examples}
  %   \begin{itemize}
  %   \item Tsukuba Coq Users's Group: regular languages, $\lambda$-calculus, arithmetic, ... (in Japanese + ssreflect)
  %   \item Software Foundations (B. Pierce \emph{et al.})
  %   \end{itemize}
  % \end{block}
\end{frame}

@@

\section{Example: Kirby \& Paris' hydras}

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}
  \frametitle{The \Hydras project}
  \begin{block}{}
    \begin{itemize}
   \item Experimental platform for the  development of \textcolor{lookcolor}{maintained} and \textcolor{lookcolor}{documented} libraries of formal proofs.
    \item A project of \community, developped on Github
      \begin{itemize}
      \item CI/CD
        \item Tools for collaboration (issues, PR, etc.)
        \end{itemize}
           \item A book in pdf (300p), generated  with \textcolor{lookcolor}{\alectr} and \LaTeX, continuously updated and deployed
    \end{itemize}
  \end{block}
  \begin{block}{Contents}
    \begin{itemize}
    \item Evolved version  of two contributions: \textcolor{plugincolor}{Cantor} and \textcolor{plugincolor}{Additions}
    \item Maintenance of \textcolor{plugincolor}{Ackermann}
      (part of Russel O'Connor's \textcolor{plugincolor}{Goedel})
    \item Bridge to \textcolor{plugincolor}{Gaia} (José Grimm) (\emph{in construction})

@@

  \begin{scope}[yshift=2.0cm, xshift=1.7cm] 
     \node[ellipse, dotted, fill=orange!20, minimum height=0.5cm,minimum width=1.5cm] (settheory) { Set theory\footnote{N. Bourbaki}};
     \node[ellipse, dotted, fill=orange!20, minimum height=0.5cm,minimum width=1.5cm, left of=settheory, node distance=8.4cm] (prooftheory) { Proof theory\footnote{K. Schutte, J. Ketonen, R. Solovay, L. Kirby \& J. Paris}};
  \node[ellipse, dotted, fill=orange!20, minimum height=0.5cm,minimum width=1.5cm, left of=settheory, node distance=4.8cm] (algo) { Algorithmics\footnote{S. Brlek \emph{et. al}}};
\end{scope}

\begin{scope}[yshift=1.0cm, xshift=-1.5cm]
   \node[rectangle, dotted, draw= black!20,fill=green!20,minimum height=0.5cm,minimum width=1.5cm] (acl2) { [ACL2]\footnote{P. Manolios \&  D. Vroon}};   
\end{scope}

@@

\draw[->] (equations) -- (hydras) ;
\draw[->] (mathcomp) -- (gaia) ;
\draw[->] (mathcomp) -- (chains) ;
\draw[->] (paramcoq.south) -- (chains) ;
\draw[->] (pockcc) -- (goedelcc) ;
\draw[dotted, ->] (prooftheory) -- (hydras);
\draw[dotted, ->] (settheory) -- (cats);
\draw[dotted, ->] (prooftheory) -- (goedel);
\draw[dotted, ->] (algo) -- (additions);
\end{tikzpicture}
}
\caption{Genealogy and dependencies for \Hydras packages.}
  \label{fig:genealogy}
\end{figure}
\end{frame}

@@

\begin{frame}
   \begin{block}{An example-driven book}
    \begin{itemize}
    \item The structure is determined by the presented topics (discrete math, algorithmics, etc.). \coq technology (formalization and proof patterns) is presented when needed.
    \item No need to be complete (there is already a reference manual)
 %   \item No need to introduce \coq (there are already a lot of initiation books and tutorials)
    \item Comparison of  different formalizations of a given notion, and several proofs of the same theorem.
      \item Show also interesting dead ends (formalization, tactics, proof structure).
    \end{itemize}
  \end{block}
  % \begin{block}{Examples}
  %   \begin{itemize}
  %   \item Tsukuba Coq Users's Group: regular languages, $\lambda$-calculus, arithmetic, ... (in Japanese + ssreflect)
  %   \item Software Foundations (B. Pierce \emph{et al.})
  %   \end{itemize}
  % \end{block}
\end{frame}

@@

\section{Kirby \& Paris' hydras}
